<small> Supplementary materials for the main submission entitled - <br><br> Clustering time series based on probability distributions across temporal granularities

### 2021-11-09 paper-supplementary.Rmd
353 customers grouping updated in supplementary

```{r}

@@

hod_group_entire1 <- data_heatmap_hod_group %>% 
  filter(group<9) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=group,
                  fill = as.factor(group), alpha = 0.5),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=group, 
                color = as.factor(group)), size = 1)+
  facet_wrap(~group, 
             scales = "free_y",  
             nrow = 8,labeller = "label_both") + 
              #labeller = labeller(xfacet = c(`1` = "Group 2", `2` = "Group 4",`3` = "Group 1",`4` = "Group 3"))
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + 
  ylab("demand (in Kwh)") + 
  theme_bw()  +
  scale_x_discrete(breaks = seq(1, 24, 3))+ 
  #theme(strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme_application() +
  scale_fill_manual(values=as.vector(polychrome(20)))+
  scale_color_manual(values=as.vector(polychrome(20)))+
  theme(legend.position = "bottom")

@@

moy_group_entire1 <- data_heatmap_moy_group %>% 
  filter(group<9) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_both",
             nrow = 8) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + 
  ylab("demand (in Kwh)") +
  theme_bw() + theme_application() +
  scale_fill_manual(values=as.vector(polychrome(20)))+
  scale_color_manual(values=as.vector(polychrome(20)))+
  theme(legend.position = "bottom")

@@

wkndwday_group_entire1 <- wkndwday_data%>% 
  filter(group<9) %>% 
  mutate(group = as.factor(group)) %>% 
  ggplot(aes(x=wknd_wday, y = general_supply_kwh)) +
  #lvplot::geom_lv(aes(fill = as.factor(group)), k=5) +
  geom_boxplot(aes(fill = group, color = group),alpha = 0.5, outlier.alpha = 0.05)+
  #geom_boxplot(outlier.size = 1) + 
  coord_cartesian(ylim = ylim1*1.05)+
  #ggridges::geom_density_ridges2(aes(x = general_supply_kwh, y = wknd_wday,fill = as.factor(group))) + coord_flip() +
#geom_boxplot(aes(fill = as.factor(group))) +
  #scale_fill_lv() +
 xlab("wknd-wday") + 
  ylab("demand (in Kwh)") +
   facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_both",
             nrow = 8) + 
  theme_bw() + theme_application() +
  scale_fill_manual(values=as.vector(polychrome(20)))+
  scale_color_manual(values=as.vector(polychrome(20)))+
  theme(legend.position = "none")

@@

```{r combined-groups-js-entire, fig.cap = "The distribution of electricity demand for the clusters across hod (a), moy (b) and wkndwday (c). It seems like group 2 and 5 have a hod pattern across its members, while group 1, 3, 5 have a moy pattern. Wknd-wday variations across groups are not distinguishable, indicating that it is not a critical variable for clustering. It is helpful to compare the summarised distributions of groups to that of individuals to confirm that the most of individuals in the group have the same characterisation."}

>>>>

```{r group-353}

@@

hod_group_entire1 <- data_heatmap_hod_group %>% 
  filter(group<9) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=group,
                  fill = as.factor(group), alpha = 0.5),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=group, 
                color = as.factor(group)), size = 1)+
  facet_wrap(~group, 
             scales = "free_y",  
             nrow = 8,labeller = "label_both") + 
              #labeller = labeller(xfacet = c(`1` = "Group 2", `2` = "Group 4",`3` = "Group 1",`4` = "Group 3"))
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + 
  ylab("demand (in Kwh)") + 
  theme_bw()  +
  scale_x_discrete(breaks = seq(1, 24, 3))+ 
  #theme(strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme_application() +
  scale_fill_manual(values=as.vector(okabe(n = 8)))+
  scale_color_manual(values=as.vector(okabe(n = 8)))+
  theme(legend.position = "bottom")

@@

moy_group_entire1 <- data_heatmap_moy_group %>% 
  filter(group<9) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_both",
             nrow = 8) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + 
  ylab("demand (in Kwh)") +
  theme_bw() + theme_application() +
  scale_fill_manual(values=as.vector(okabe(n = 8)))+
  scale_color_manual(values=as.vector(okabe(n = 8)))+
  theme(legend.position = "bottom")

@@

wkndwday_group_entire1 <- wkndwday_data%>% 
  filter(group<9) %>% 
  mutate(group = as.factor(group)) %>% 
  ggplot(aes(x=wknd_wday, y = general_supply_kwh)) +
  #lvplot::geom_lv(aes(fill = as.factor(group)), k=5) +
  geom_boxplot(aes(fill = group, color = group),alpha = 0.5, outlier.alpha = 0.05)+
  #geom_boxplot(outlier.size = 1) + 
  coord_cartesian(ylim = ylim1*1.05)+
  #ggridges::geom_density_ridges2(aes(x = general_supply_kwh, y = wknd_wday,fill = as.factor(group))) + coord_flip() +
#geom_boxplot(aes(fill = as.factor(group))) +
  #scale_fill_lv() +
 xlab("wknd-wday") + 
  ylab("demand (in Kwh)") +
   facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_both",
             nrow = 8) + 
  theme_bw() + theme_application() +
  scale_fill_manual(values=as.vector(okabe(n = 8)))+
  scale_color_manual(values=as.vector(okabe(n = 8)))+
  theme(legend.position = "none")

@@

```{r combined-groups-js-entire, fig.cap = "The distribution of electricity demand for the clusters across hod, moy and wkndwday for the $17$ groups from $353$ customers. Wknd-wday variations across groups are not distinguishable, but ideally each group should have an unique combination of hod and moy.", fig.height=6}
